A comparison of different methods for calculating tangent-stiffness matrices in a massively parallel computational peridynamics code.

### 2013-10-28 jacobian_calc_CMAME.tex
More qoi section fixes

The other goal was to compare the four methods, that is including AD, on the basis of speed. Instead of convergence rate being measured, speed of iteration was measured because it could be so done at the same time as accuracy was being measured given a single tangent-stiffness calculation.  It was assumed that the order that each method was evaluated was unimportant, that evaluating each method sucessively within each solver iteration did not affect their performance individually and that speed of computation did not change with time. These assumptions allowed the test program to run the
same problem with each of the methods at effectively the same time and generate an equal volume of data from each method. It was also assumed that the tangent-stiffness matrix calculation time for each of the methods did not vary based on what values the independent variables held, as they do from iteration to iteration as the Newton solution iterate is updated.  This assumption allowed calculation time measurements to be averaged over all iterations within a solution attempt. The purpose of averaging calculation time measurements was to informally address the extraneous variables of evaluation order and computer system load due to system processes not associated with the study. The question is begged: if it is assumed that the value of independent variables had no effect on iteration speed, then why couldn't each of the method have been run independently so that convergence data were recorded, so long as system being solved was the same? The answer is that this would have made accuracy comparisons invalid if measured concurrently with convergence
rate, while it would cost additional time and resources if convergence rate were measured in serparate runs. Instead, while not part of the study, the example programs available on the
corresponding author's website allow the reader to make a comparison of the methods for themselves
on the basis of accuracy and convergence rate for two example nonlinear systems. In the examples,
notice how convergence rate decreases when the step size selected for forward-difference or
complex-step is set to larger numbers such that accuracy relative to AD is decreased.

>>>>

The other goal was to compare the four methods, that is including AD, on the basis of speed. Instead of convergence rate being measured, speed of iteration was measured because it could be so done at the same time as accuracy was being measured given a single tangent-stiffness calculation.  It was assumed that the order that each method was evaluated was unimportant, that evaluating each method sucessively within each solver iteration did not affect their performance individually and that speed of computation did not change with time. These assumptions allowed the test program to run the
same problem with each of the methods at effectively the same time and generate an equal volume of data from each method. It was also assumed that the tangent-stiffness matrix calculation time for each of the methods did not vary based on what values the independent variables held, as they will from iteration to iteration as the Newton solution iterate is updated.  This assumption allowed calculation time measurements to be averaged over all iterations within a solution attempt. The purpose of averaging calculation time measurements was to informally address the extraneous variables of parallel evaluation order and computer system load due to system processes not associated with the study. While not part of the study, the example programs available on the corresponding author's website allow the reader to make a comparison of the methods for themselves on the basis of accuracy and convergence rate for two example nonlinear systems. In the examples, one will notice that the forward-difference method will lose quadratic convergence when the step size selected too large such that accuracy relative to AD is decreased.
